Pre-registration details

### 2019-05-13 analysis/preregistration.Rmd
Cross out CNU and GSU for now
Make preregistration link live

<p><a href="https://osf.io/dx973/register/565fb3678c5e4a66b5582f67" class="btn btn-md btn-success disabled" target="_blank" role="button">
<i class="fa fa-pencil-square" aria-hidden="true"></i>&nbsp;
OSF preregistration protocol &raquo;
</a></p>

@@

This project has received IRB approval from the human subjects research committees at BYU, Georgia State, and Christopher Newport. We have included a generic version of our protocol below.

>>>>

<p><a href="https://osf.io/hsbyd" class="btn btn-md btn-success" target="_blank" role="button">
<i class="fa fa-pencil-square" aria-hidden="true"></i>&nbsp;
OSF preregistered pre-analysis plan &raquo;
</a></p>

@@

This project has received IRB approval from the human subjects research committees at BYU, ~~Christopher Newport, and Georgia State~~. We have included a generic version of our protocol below.
